---
output: github_document
---

```{r options, echo=FALSE}
library(knitr)
opts_chunk$set(warning=FALSE)
```

# coalitions

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active) 
[![Travis-CI Build Status](https://travis-ci.org/adibender/coalitions.svg?branch=master)](https://travis-ci.org/adibender/coalitions)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/adibender/coalitions?branch=master&svg=true)](https://ci.appveyor.com/project/adibender/coalitions)
[![Coverage Status](https://codecov.io/github/adibender/coalitions/master.svg)](https://codecov.io/github/adibender/coalitions?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/coalitions)](https://cran.r-project.org/package=coalitions)

**Calculate oalition probabilities in multi-party democracies**

## Overview 
The package offers functions that calculate coalition probabilities 
in multi-party elections, based on a survey results. 
It offers two main functions:

- `get_surveys`: Scrapes surveys on German Bundestag elections from [wahlrecht.de](http://www.wahlrecht.de)
- `get_probabilities`: Calculates coalition probabilities based on provided survey results. 

## Installation
Install from GitHub using: 
```{r, eval=FALSE}
devtools::install_github("adibender/coalitions", build_vignettes=TRUE)
```


## Usage

Detailed workflow is outlined in the vignettes enclosed in the package, 
especially in `vignette("workflow", package="coalitions")`.


### Scrape surveys
The wrapper `get_surveys()` which takes no arguments, downloads all surveys currently available at [wahlrecht.de](http://www.wahlrecht.de/umfragen) and stores them in a nested `tibble`: 

```{r, message = FALSE}
library(coalitions)
library(dplyr)
library(tidyr)
surveys <- get_surveys()
surveys
```

Each row represents a survey insitute and each row in the `surveys` column again contains a nested `tibble` with survey results from different time-points: 

```{r}
surveys %>% 
    filter(institute == "allensbach") %>% 
    unnest()

survey <- surveys %>% unnest() %>% slice(1)
survey
```

### Calculate coalition probabilities
For each survey (row) we can calculate the coalition probabilities

```{r}
survey %>% get_probabilities(nsim=1e4) %>% unnest()
```
