---
title: "Pooling"
author: "Alexander Bauer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pooling}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo = FALSE}
library(knitr)
opts_chunk$set(
  fig.align  = "center",
  fig.width  = 4,
  fig.height = 4,
  warning    = FALSE,
  crop       = TRUE)
```


```{r message=FALSE, warning=FALSE}
library(tidyr)
library(purrr)
library(dplyr)
library(coalitions)
```


In this vignette we demonstrate the offered functionality for pooling
multiple surveys.


## Overview
We offer convenience functions that allow for easily performing the pooling
approach:

1. `get_surveys`: Wrapper that uses `scrape_wahlrecht` and `collapse_parties`
to download the most current survey results from https://www.wahlrecht.de/
and stores the prepared data inside a nested `tibble` (see `tidyr::nest`)

2. `pool_surveys`: Pool all newest surveys (obtained with `get_surveys`), using
a specified time window that defaults to the last 14 days, and assuming a certain
correlation between the number of party-specific votes of any two polling agencies,
which defaults to 0.5. Per polling agency only the newest survey in the time windows
is considered.


## Setting the time window
The three arguments `last_date`, `period` and `period_extended` define the time window
used in `pool_surveys`. Using these arguments one can choose between two types of pooling:

1. If `period_extended` equals `NA`: Surveys in the time window from `last_date` to
`last_date - period` will be considered for each polling agency.

2. If `period_extended` does not equal `NA`: Same as 1. Additionally however, surveys in the time
window from `last_date - period` to `last_date - period_extended` will also be considered
for each polling agency, but only after downweighting them by halving their
true sample size.

The latter option can be especially useful if opinion polls for a specific election
are only published very rarely. As default, `pool_surveys` uses a time window starting
from the current date and going 14 days back, not making use of `period_extended`.



## Read data
```{r}
# Scrape current surveys from the major polling agencies in Germany
# surveys <- get_surveys()
# As the web connection is sometimes a bit unstable we here use the sample data set of pre-scraped surveys
surveys <- coalitions::surveys_sample
surveys
```

## Perform pooling
```{r}
# Obtain the pooled sample for today, based on the last 14 days
last_date <- surveys %>% tidyr::unnest() %>% pull(date) %>% max()
pool <- pool_surveys(surveys, last_date = last_date)
pool %>% select(-start, -end)
```
