---
title: "Workflow"
author: "Andreas Bender"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo = FALSE}
library(knitr)
opts_chunk$set(
  fig.align  = "center",
  fig.width  = 4,
  fig.height = 4,
  warning    = FALSE,
  crop       = TRUE)
```


```{r message=FALSE, warning=FALSE}
library(tidyr)
library(purrr)
library(dplyr)
library(coalitions)
```


In this vignette we demonstrate the basic workflow using the most recent
*Emnid* survey.

## Overview
This package calculates coalition probabilities in multi-party systems.
To this end we provide some convenience functions, the most important of which
are listed below:

1. `scrape_wahlrecht`: A wrapper function that download the most current
survey results from http://www.wahlrecht.de/

2. `collapse_parties`: Transforms information on percentages received by
individual parties in long format and stores them inside a nested tibble
(see `tidyr::nest`)

3. `draw_from_posterior`: Draws `nsim` samples from the posterior distribution
(i.e. `nsim` simulated election results based on provided survey)

4. `get_seats`: Obtain seat distributions for each simulation (see also `?sls`)

5. `have_majority`: Given a list of coalitions of interest, calculates if the
respective coalition would have enough seats for a majority

6. `calculate_probs`: Given majority tables obtained from `have_majority`, calculates the probabilities for the respective coalitions to have enough
seats for a majority


## Read in data
```{r}
# one line per survey (party information in wide format)
emnid <- scrape_wahlrecht() %>% slice(1:6)
emnid %>% select(-start, -end)
```

## Collapse survey data
After applying `collapse_parties` we still have one row per survey,
but information on parties and percentage of votes they received is
stored in a long format in a separate column (see `?tidyr::nest`):

```{r}
elong <- collapse_parties(emnid)
head(elong)
elong %>% slice(1) %>% select(survey) %>% unnest()
```

## Simulate elections
Based on each survey we can now simulate `nsim` elections by drawing from the
Dirichlet distribution

```{r}
set.seed(1)     # for reproducibility

elong <- elong %>%
  mutate(draws = map(survey, draw_from_posterior, nsim=10, correction=0.005))
elong %>% select(date, survey, draws)
# each row is one election simulation
elong %>% slice(1) %>% select(draws) %>% unnest()
```


## Calculate seat distribution
Given the simulated elections, we can calculate the number of seats each
party obtained. To do so we need to have a function that knows how to
redistribute seats for the particular election. In Germany for example,
seats are distributed according to the system of *Sainte-Lague-Scheppers*, which
is implemented in `?sls`.

This makes this package easily extensible to other
multi-party systems, as you only need to provide a function that redistributes
seats based on percentages obtained by the various parties and provide that
function to the `distrib.fun` argument of the `get_seats` function:


```{r}
elong <- elong %>%
  mutate(seats = map2(draws, survey, get_seats, distrib.fun=sls))
elong %>% select(date, survey, draws, seats)
## sim column indicates simulated elections (rows in draws column)
elong %>% slice(1) %>% select(seats) %>% unnest()
```

In the above example, given the latest survey, CDU/CSU would have `r elong %>% slice(1) %>% select(seats) %>% unnest() %>% filter(party == "cdu" & sim == 1) %>% pull(seats)` seats
in the first simulation, `r elong %>% slice(1) %>% select(seats) %>% unnest() %>% filter(party == "cdu" & sim == 2) %>% pull(seats)` seats in the second simulation, etc.


## Calculate majorities
The next step is to define coalitions of interest, then calculate in what
percentage of the simulations the coalition would obtain enough seats for
a majority.

Below, each list element defines one coalition of interest (one party
could potentially obtain absolute majority on their own):

```{r}
coalitions <- list(
	c("cdu"),
	c("cdu", "fdp"),
	c("cdu", "greens"),
	c("cdu", "fdp", "greens"),
	c("spd"),
	c("spd", "left"),
	c("spd", "greens"),
	c("spd", "left", "greens"),
	c("cdu", "spd"))


elong <- elong %>%
	mutate(majorities = map(seats, have_majority, coalitions=coalitions))
elong %>% select(date, draws, seats, majorities)
# The majorities table for each date will have 1 row per simulation
# and one column per coalition
elong %>% slice(1) %>% select(majorities) %>% unnest()
```


## Calculate coalition probabilities

The last step is to calculate the coalition probabilities (note that
by default we exclude "superior" coalitions, i.e. if "cdu/csu" have a majority
on their own, this simulation will not be counted to the simulation with
majority for "cdu/csu" and "fdp", see example in `?calculate_probs`):

```{r}
elong <- elong %>%
	mutate(
		probabilities = map(majorities, calculate_probs, coalitions=coalitions))
elong %>% select(date, majorities, probabilities)
# one row per coalition
elong %>% slice(1) %>% select(probabilities) %>% unnest()
```


## Wrapper
There is a wrapper function that directly returns probabilities:

```{r}
elong <- collapse_parties(emnid)
elong %>% get_probabilities(., nsim=10) %>% unnest()
```
